Case for Support

### 2021-11-16 application/detailsOfResource.tex

As it stands, Bonsai is designed to be extensible and is distributed with a package management framework that controls installation of both optional core packages and user-contributed extensions.
%
However, the present framework requires extensions to be written in Bonsai's native C\# programming language.
%
This specificity restricts the number of potential contributors to the ecosystem.
%
It also hinders easy incorporation of published analytic tools, many of which are implemented for interpreted language systems such as Python, R, or MATLAB.

>>>>

As it stands, Bonsai is designed to be extensible and is distributed with a package-management framework that controls installation of optional core packages as well as user-contributed extensions.
%
However extensions must be written in Bonsai's native C\# programming language.
%
This specificity restricts the range of potential contributors to the ecosystem.
%
It also hinders easy incorporation of published analytic tools, many of which are implemented within other interpreted language systems such as Python, R, or MATLAB.

### 2021-11-16 application/trackRecord.tex

The team responsible for the proposed project comprises two academic
institutes, the Gatsby Computational Neuroscience Unit (GCNU) and the Sainsbury
Wellcome Centre for Neural Circuits and Behavior (SWC), and a private
collaborator, NeuroGEARS Ltd.

The GCNU is a world-class research center for computational neuroscience and
machine learning, while the Sainsbury Wellcome Center is a top-notch experimental
neuroscience research center. They share a common building and collaborative
activities are at the heart of both institutes.
%
NeuroGEARS is a spinoff of the SWC and is currently contributing to a major
collaborative research project between the SWC and the GCNU. It has developed
Bonsai, a very unique ecosystem for experimental control and data acquisition,
it has offered courses around the globe instructing students on advanced
experimental control, and has used Bonsai in numerous research and private
experimental projects. Thus, NeuroGEARS has extensive experience on the
implementation of neuroscience experiments.

>>>>

The team responsible for the proposed project comprises two academic
institutes at University College London, the Gatsby Computational Neuroscience Unit (GCNU) and the Sainsbury
Wellcome Centre for Neural Circuits and Behaviour (SWC), and a private
collaborator, NeuroGEARS Ltd.

The GCNU is an authority in computational neuroscience and
machine learning, while the Sainsbury Wellcome Centre is a world-leading experimental
neuroscience research institute. They share a common building, which facilitates regular interaction and collaboration across various research groups, including the two named PIs in this project, and also collaborate in many joint activities.
%
NeuroGEARS is a spinoff of the SWC and is currently contributing to a major
collaborative research project between the SWC and the GCNU. It developed
Bonsai, a unique ecosystem for experimental control and data acquisition,
and offers courses around the globe instructing students on advanced
experimental control. NeuroGEARS has used Bonsai in numerous research and private experimental projects, and has extensive experience on the
implementation of neuroscience experiments.
